Trends of SDR in Thessaloniki

### 2023-07-10 Article.Rmd
Commit 2023-07-10 12:11

Although, using the cumulative sums plots we can reveal some structure within the trends and some difference between the sky conditions [@Regier2019]. 
On all three plots on Figure\ \ref{fig:cumsum}, we observe a step downward part in the begin of the period until about 2000, an almost steady part until about 2016 for All-sky and Clear-sky conditions (Figures\ \ref{fig:cumsum-1}, \ref{fig:cumsum-2}), and until 2009 for Cloud-sky conditions (Figure\ \ref{fig:cumsum-3}), and finally, a steep upward part until the present.
For a more uniform trend we expect the cumulative sum plot of the anomaly, to have a symmetric 'V' shape.
In this case......

suspected stagnend period

Comparining the conditions

Variability issues

@@

## Long term trends by Solar zenith angle.

>>>>

Although, using the cumulative sums plots we can reveal some structure within the trends and some difference between the sky conditions [@Regier2019]. 
On all three plots on Figure\ \ref{fig:cumsum}, we observe a step downward part in the begin of the period until about 2000, an almost steady part until about 2016 for All-sky and Clear-sky conditions (Figures\ \ref{fig:cumsum-1}, \ref{fig:cumsum-2}), and until 2009 for Cloud-sky conditions (Figure\ \ref{fig:cumsum-3}), and finally, a steep upward part until the present.
For a more uniform trend, we expect the cumulative sum plot of the anomaly, to have a symmetric 'V' shape.
In our case, for all sky conditions we observe a period where the cumulative remain relative steady.
This indicates, that the anomaly was evenly distributed around the climatological mean.
Another distinct feature of the cumulative plots, is the difference, between the sky conditions, of the start of the sums sudden increase, for the latter part of the period.
This can make us to suspected that clear-Sky conditions SDR and cloud-sky SDR is affected by different mechanisms.

@@

## Effects of the solar zenith angle on SDR.

.... cite paper low elevation SDR .....

The relative position of the Sun in the sky, seem to be a major drive of the attenuation of SDR, as it is affect

... Aerosols and clouds ...
